---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# lefse

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html#experimental)
[![CRAN\_Status\_Badge](http://www.r-pkg.org/badges/version/lefse)](https://cran.r-project.org/package=lefse)
<!-- badges: end -->

The goal of **lefse** is to utilizing phylogenetic and functional information for the analyses of ecological datasets. The analyses include methods for quantifying the phylogenetic and functional diversity of assemblages.

## Installation

You can install the development version of lefse like so:

``` r

remotes::install_github("PaulESantos/lefse")

```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(lefse)
# data
data("lefse_sample")
data("lefse_traits")
# Moments
lefse::com.trait.moments(lefse_sample, lefse_traits)
# 
lefse::com.trait.weighted(lefse_sample, lefse_traits)
#
lefse::trait.range(lefse_sample, lefse_traits)
```

